\documentclass{article}
\title{Savory Stuffed Cabbage Rolls}
\date{\vspace{-5ex}}
\pagenumbering{gobble}
\usepackage[margin=0.5in]{geometry}
\begin{document}
\maketitle

Shop

\begin{itemize}
\item 1 medium head cabbage
\item 1 pound ground beef
\item 1/2 cup chopped onion
\item 3 T uncooked brown rice
\item 2 T chopped fresh parsley (2 t dried)
\item 2 t salt
\item 1/2 t pepper
\item 1 egg
\item 1 3/4 cups plain tomato sauce
\item 1 cup canned tomato chunks
\item 2 T honey
\item 1/2 cup grated Colby cheese, optional
\end{itemize}

Cook

\begin{enumerate}
\item Put the head of cabbage in a pot. Cover with water. Remove the cabbage and bring the water to a boil. Turn off the heat. Submerge the whole head of cabbage in the boiling water and cover. Let sit for 15-20 minutes.
\item Meanwhile, brown the beef and onion. Turn off the heat. Add the rice, parsley, salt, pepper, and egg.
\item When the cabbage is done “cooking”, remove it from the water onto a cookie sheet with sides (to catch any remaining water). Very carefully, remove 12 leaves. Cut the thickest part of center rib out of each leaf, about 1 or 2 inches. There will be a little V in the middle of each leave. Divide the meat filling between the leaves and roll up jelly roll fashion, but tucking in the ends so the filling stays put. Place the rolls in a deep casserole dish.
\item Pour the tomato sauce, tomato chunks, and honey over the rolls. Cover and bake at 350 for about an hour and a half. Remove the lid, sprinkle with cheese, and bake another 5 minutes or until cheese is melted. Let set a few minutes before serving.
\end{enumerate}

Serves: 4 – 6
Derived from https://zoedawn.wordpress.com/2011/06/24/savory-stuffed-cabbage-rolls/
\end{document}
